A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-16 ms.Rmd
some minor work on discussion

# DISCUSSION
Niche breadth, as measured by different types of generalism, was significantly associated with urbanization in our analysis. This result was robust across non-phylogenetic and phylogenetic models, model averaging approaches, and across phylogenetic uncertainty. Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding specialist species [@sorace2009distribution]. As such, future urban development aimed at increasing avian diversity in urban areas should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat], with a focus on intact vegetation [@sushinsky2013should] connected by corridors [@litteral2017role]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Lastly, a focal point should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn increase the presence of insectivorous bird species in urban environments.

The non-random distribution of the urbanization index across the phylogeny (Table 1) contrasts with previous studies [@evans2011makes], but this contrasting finding is likely a result of increased statistical power from our larger sample size: 477 species in this study compared with 55 species in Evans *et al.* [-@evans2011makes]. It's not surprising that a larger sample size finds a non-random pattern in urbanization across the bird phylogeny and we demonstrated the importance of treating species as non-independent by considering phylogeny in the context of the linear model. For example, some predictor variables became less crucial in the phylogenetically controlled models compared with the non-phylogenetic models, including some feeding types (i.e., insect specialists) and habitat preferences (i.e., agricultural). For these variables, it is likely that there may be particular clades which include a number of species that are associated with both that particular trait and urbanization [see @felsenstein1985confidence]. Conversely, some of the most important predictor variables (e.g., clutch size and feeding habitat generalism; Figures 4 and 5) showed a stronger relationship (i.e., increased parameter estimates) with urbanization when phylogeny was accounted for, and this affect was robust relative to a consideration of phylogenetic uncertainty (Fig. S2). Furthermore, residual brain mass (and body size to a lesser extent) was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade the species with the largest residual brain mass [@maklakov2011brains] and largest body size [@major2010museum] are most suited to surviving in urban areas. While some studies have found a lack of evidence that relative brain size is critical in urban birds [@kark2007living; @evans2011makes], our results suggest that brain size is indeed heavily correlated with urban birds [@moller2009successful; @maklakov2011brains; @moller2015brain]. This finding highlights the necessity to investigate these relationships in a phylogenetically informed manner. Lastly, it is worth noting that these results are consistent with the observation of reduced phylogenetic diversity in urban areas [@la2018phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence; @ibanez2017global; @sol2017urbanisation; @major2010museum].

@@

We provide the largest study to date using a continuous urbanization metric in order to assess ecological and life history traits which are associated with a species' adaptability to urban environments. Our results suggest that generalist species, with large relative brain size, are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. This work should be extended to test whether our findings can accurately predict species which are commonly found in urban environments in other parts of the world, based on a known suite of traits associated with a given set of species. Australia is a relatively young country with rapid urbanization currently underway [@coffee2016visualising] and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [@hallmann2017more]. Furthermore, future studies should focus on broad-scale data to form generalizable patterns which rely on continuous measures for improved predictive performance.

>>>>

# DISCUSSION
Niche breadth, as measured by different types of generalism, was significantly associated with urbanization in our analyses, evidenced by the robustness of this result across non-phylogenetic and phylogenetic models, model-averaging approaches, and across phylogenetic uncertainty (Fig. S2). Conversely, specialized feeding strategies were negatively associated with urbanization: granivorous and insectivorous specialists were much less likely to be found in urban environments. These results suggest that urbanization is, in general, excluding specialist species [@sorace2009distribution]. As such, future urban development aimed at increasing avian diversity in urban areas should focus on maintaining a high diversity of habitat [@melles2003urban] both for foraging [@shochat2004linking], and nesting [@fernandez2001habitat], with a focus on intact vegetation [@sushinsky2013should] connected by corridors [@litteral2017role]. A species-specific approach to assess particular resources necessary for specialist species may be necessary [@fernandez2004spatial]. Furthermore, a focal point of avian biodiversity conservation should be on increasing insect abundance and diversity in urban environments [@baldock2015uk], which will in turn benefit avian biodiversity in urban environments.

The non-random distribution of the urbanization index across the phylogeny (Table 1) is consistent with the observation of reduced phylogenetic diversity in urban areas [@la2018phylogenetic], suggesting that there are phylogenetic constraints which allow certain birds to persist within urban environments [@morelli2016evidence; @ibanez2017global; @sol2017urbanisation]. This finding of a strong phylogenetic signal contrasts with previous studies [@evans2011makes], but this is likely a result of increased statistical power from our larger sample size: 477 species in this study compared with 55 species in Evans *et al.* [-@evans2011makes]. It's not surprising that a larger sample size finds a non-random pattern in urbanization across the bird phylogeny and we demonstrated the importance of treating species as non-independent by considering phylogeny in the context of the linear models. For example, some predictor variables became less crucial in the phylogenetically controlled models compared with the non-phylogenetic models, including some feeding types (i.e., insect specialists) and habitat preferences (i.e., agricultural). For these variables, it is likely that there may be particular clades which include a number of species that are associated with both that particular trait and urbanization [see @felsenstein1985confidence]. Conversely, some of the most important predictor variables (e.g., clutch size and feeding habitat generalism; Figures 4 and 5) showed a stronger relationship (i.e., increased parameter estimates) with urbanization when phylogeny was accounted for, and this affect was robust relative to a consideration of phylogenetic uncertainty (Fig. S2). Furthermore, residual brain mass (and body size to a lesser extent) was significantly important within the phylogenetic models, but not in the non-phylogenetic models, suggesting that within a clade the species with the largest residual brain mass [@maklakov2011brains] and largest body size [@major2010museum] are most suited to surviving in urban areas. While some studies have found a lack of evidence that residual brain size is an important predictor in urban birds [@kark2007living; @evans2011makes], our results suggest that residual brain size is indeed heavily correlated with urbanization in birds [@moller2009successful; @maklakov2011brains; @moller2015brain]. This finding highlights the necessity to investigate the trait-urbanization relationships in a phylogenetically informed manner.

@@

We provide the largest study to date using a continuous urbanization index to assess ecological and life history traits which are associated with a species' adaptability to urban environments. Our results suggest that generalist species, with large residual brain size, are better prepared to forage and survive in the ecologically novel aspects of urban environments [@shochat2006patterns]. We highlight that future studies investigating the trait-urbanization relationship should focus on broad-scale data  to form generalizable patterns which rely on continuous measures for improved predictive performance. This work should be further extended to test whether our findings can accurately predict species which are commonly found in urban environments in other parts of the world, based on a known suite of traits associated with a given set of species. In the context of our specific findings, Australia is a relatively young country with rapid urbanization currently underway [@coffee2016visualising] and fully understanding how birds respond to urban development is critical to inform future management. Urban avian biodiversity could be increased by improving the suitability of foraging for granivores and insectivores, especially important given the recent noted collapse of insects in other parts of the world [@hallmann2017more].
